### 2020-04-13 serial.tex
intro

Here, we provide an answer to this decade-old paradox.
We develop a novel framework for understanding serial intervals and show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.

>>>>

Here, we provide an answer to this decade-old paradox.
We develop a novel framework for understanding serial intervals and show that the serial-interval distribution must be defined with reference to disease incidence;
previous frameworks implicitly assume that incidence remains constant.
Using our framework, we are able to show that both serial- and generation-interval distributions give identical estimates of $\mathcal R$ during the exponential growth phase of an epidemic.
However, failing to account for changes in the serial-interval distributions over time can severely bias the estimate of $\mathcal R$.
We apply our framework to serial intervals of COVID-19 and lay out several principles to consider in using serial intervals in the analysis of the ongoing pandemic.
